\documentclass[12pt, letterpaper, oneside]{article}

\title{\textbf{Statement of Purpose}}
\author{Tran Phong Binh\thanks{Email: \texttt{phongbinh2511@gmail.com}}}
\date{\today}

\begin{document}

\maketitle

Here is progress I made at National Tsing Hua University: As soon as I joined HSCC Lab, I entered Delta Electronics's anomaly detection project, researching three papers on Bayesian optimization, implementing Gaussian Process Hedge algorithm, and presented four articles on Generative Adversarial Network (GAN). Additionally, I enrolled in five Computer Science courses with at least four top class A+, whilst grading homeworks and monitoring exams as teaching assistant for Design and Analysis of Algorithms lectured by Chair Professor Jang-Ping Sheu. Moreover, I pushed hard on self-learning, progressing 50\%, 75\%, and 100\% in Stanford's Convex Optimization, MIT's Artificial Intelligence, and MIT's Linear Algebra courses, respectively. For Master's thesis, I studied 16 publications in 5G scheduling, narrowing research topic to resource allocation in ultra-reliable low latency communications (URLLC) puncturing systems, inventing an approximation algorithm by total unimodularity, and have been working on simulations\footnote{\texttt{https://github.com/phogbinh/5g}}.

I mark three prime goals for next semester: finishing course credits, reading 80 academic papers, completing thesis's simulations. Firstly, I attend Natural Language Processing Lab. by Professor Jyun-Sheng Chang to experiment learning-based techniques on my research problem. Secondly, I take on five papers and discuss with my Professor once per week. Thirdly, I kickstart thesis writing, finalizing simulation environment to reproduce others' work and compare performances, aiming to publish on IEEE conferences like INFOCOM and ICC.

\end{document}
